---
title: "Hobo PT QAQC"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE)
# Explanation of code
## Action required

#Install and/or load packages
#install.packages('ggplot2')
#install.packages('plotly')
#install.packages('tidyverse')

library(ggplot2)
library(plotly)
library(tidyverse)
library(knitr)
library(lubridate)

## Set working directory
setwd("~/git-repos/wx-tools/data_input")

```


```{r load pt data, include=FALSE}

#pull in data from folder
# Load data - read headers
fileheaders <- read.csv("626_PT_20409274_20230508_corrected.csv",
                        nrows = 1, as.is = TRUE,
                        header = FALSE)
# Read in data, drop redundant header rows
df <- read.csv("626_PT_20409274_20230508_corrected.csv",
                 header = FALSE,
                 skip = 4,
                 stringsAsFactors = FALSE)

# Add headers to dataframe
colnames(df) <- fileheaders
names(df)
glimpse(df)


#assign new column names
names(df) <- c("NA","Date", "abs_pres", "temp","pres", "watlev")
names(df)

#Drop by column position
df = select(df, -c(1))

#set date format
df$Date<-as.POSIXct(df$Date,format="%Y-%m-%d %H:%M")

```


```{r qc_flagging, include = FALSE}

data_flagged<-watlev %>% 
  mutate(depth_diff = lead(`hyac-depth`)-lag(`hyac-depth`), #computes difference between depths
         flag = if_else(depth_diff>0.02, "SVC", "AV"), #flags based on maximum allowable depth change per time interval
         temp_diff = lead(`hyac-twtr`)-lag(`hyac-twtr`), #computes difference between temps
         flag = if_else(temp_diff>2, "SVC", "AV"), #flags based on maximum allowable temp change per time interval
         flag = if_else(`hyac-twtr`< 0, "SVC", "AV"), #flags based on min temp -- potential for freezing
         flag = if_else(Date>="2022-09-11 02:10:00"& Date<="2022-09-28 12:00:00", "SVC", "AV")) %>% #date range for unusual stage drop
       select(-depth_diff, -temp_diff) #remove unneeded columns 


data_SVC <- data_flagged %>% 
  filter(flag == 'SVC')
data_AV <- data_flagged %>% 
  filter(flag == 'AV')
```

## Hobo PT network 

Two Onset Hobo U20L-04 pressure transducers (one measuring water pressure and one measuring air pressure) were installed 2018-08-27 to support the existing stage sensor network and serve as a bakcup in the event of a sensor failure or power issue with the network. The sensors log on 30 minute intervals and are downloaded twice per year. This dataset reflects the current time series and contains  `r nrow(data)` measurements of which `r nrow(data_SVC)` are flagged as suspicious, while `r nrow(data_AV)` are flagged as accepted. 24hr rainfall data from the Quadra station has been qc'd outside of this document up-to-date to October 2022, and is displayed on the Hakai sensor network.

`r paste("First created on 2023-05-08. Updated on", Sys.Date())`

```{r qc_flagging, include = FALSE}

data_flagged<-df %>% 
  mutate(depth_diff = lead(df$watlev)-lag(df$watlev), #computes difference between depths
         flag = if_else(depth_diff>0.02, "SVC", "AV"), #flags based on maximum allowable depth change per time interval
         temp_diff = lead(df$temp)-lag(df$temp), #computes difference between temps
         flag = if_else(temp_diff>2, "SVC", "AV"), #flags based on maximum allowable temp change per time interval
         flag = if_else(df$temp< 0, "SVC", "AV"))

data_SVC <- data_flagged %>% 
  filter(flag == 'SVC')

data_AV <- data_flagged %>% 
  filter(flag == 'AV')
```

##### Water Level
```{r plot-watlev, include=TRUE}

plot_ly(df, x = ~Date, y = ~`watlev`, 
        type = 'scatter', 
        mode = 'lines') %>%
  layout(title = " ", #barmode = 'stack',
         xaxis = list(title = "Date"),
         yaxis = list(side="left", title = 'Water Level (m)'))
         

```

##### Water Temperature
```{r plot-temp, include=TRUE}

plot_ly(df, x = ~Date, y = ~`temp`, 
               type = 'scatter', mode = 'lines', name = 'Hyac-Twtr') %>%
  layout(title = " ", #barmode = 'stack',
         xaxis = list(title = "Date"),
         yaxis = list(side="left", title = ' '))

```




