
---
title: "Sensor 2 Correction to Sensor 3 Report"
author: "Emily"
date: "`r Sys.Date()`"
output: html_document
---

## Introduction

This report details the steps taken to correct **Sensor 2** values based on **Sensor 3** readings. The process involves identifying overlapping periods between the two sensors, building a regression model to predict **Sensor 2** based on **Sensor 3**, and assessing the accuracy of the correction through various metrics.

## Data Overview

The dataset consists of water temperature readings from multiple sensors. For this analysis, **Sensor 2** and **Sensor 3** are of interest. **Sensor 1** has been excluded from the analysis due to lack of overlap with **Sensor 3**.

```{r}
# Loading necessary libraries
library(dplyr)
library(ggplot2)
library(Metrics)  # For RMSE and MAE
library(tidyr)    # For gather function
```

## Step 1: Data Preprocessing

The dataset was loaded, and column names were standardized to reflect **Sensor 2** and **Sensor 3**:

```{r}
# Data preprocessing and column renaming
colnames(df)[2] <- "sensor2"
colnames(df)[3] <- "sensor3"
```

We identified overlapping periods where both **Sensor 2** and **Sensor 3** had non-missing values.

```{r}
df_overlap <- df %>% filter(!is.na(sensor2) & !is.na(sensor3))
```

## Step 2: Building the Regression Model

A linear regression model was built to predict **Sensor 2** values based on **Sensor 3** values. This model assumes that **Sensor 3** represents the "true" temperature values, and we aim to correct **Sensor 2** to match **Sensor 3**.

```{r}
# Build regression model to correct sensor2 based on sensor3
model <- lm(sensor3 ~ sensor2, data = df_overlap)
summary(model)
```

The performance of the model was evaluated using **R²**, **RMSE**, and **MAE** metrics:

```{r}
# Model performance evaluation
evaluate_model <- function(model, actual, predicted) {
  r2 <- summary(model)$r.squared
  rmse_val <- rmse(actual, predicted)
  mae_val <- mae(actual, predicted)
  list(R2 = r2, RMSE = rmse_val, MAE = mae_val)
}

performance <- evaluate_model(model, df_overlap$sensor3, predict(model, newdata = df_overlap))
performance
```

### Model Performance
- **R²**: `r performance$R2`
- **RMSE**: `r performance$RMSE`
- **MAE**: `r performance$MAE`

These metrics show the strength of the model in predicting **Sensor 2** from **Sensor 3**.

## Step 3: Correcting Sensor 2

We used the model to correct **Sensor 2** values where they were missing. The corrected values were stored in a new column `sensor2_corrected`.

```{r}
df <- df %>%
  mutate(sensor2_corrected = ifelse(is.na(sensor2), predict(model, newdata = df), sensor2))
```

## Step 4: Residual Analysis

The residual plot for **Sensor 2** vs **Sensor 3** was generated to evaluate the model's performance. The residuals indicate how well the model's predictions align with the actual values.

```{r}
# Residual plot
ggplot(df_overlap, aes(x = sensor2, y = sensor3 - predict(model, newdata = df_overlap))) +
  geom_point(size = 1, alpha = 0.4) +
  geom_hline(yintercept = 0, linetype = 'dashed', color = 'red') +
  labs(title = 'Residual Plot: Sensor 2 vs Sensor 3', x = 'Sensor 2', y = 'Residuals') +
  theme_minimal()
```

## Step 5: Visualization of Corrected Sensor 2

The time series of **Sensor 2**, **corrected Sensor 2**, and **Sensor 3** was plotted to visually compare the corrected values.

```{r}
df_long <- df %>%
  gather(key = 'sensor', value = 'temperature', sensor2, sensor2_corrected, sensor3)

df_long_filtered <- df_long %>%
  filter(sensor %in% c('sensor2', 'sensor2_corrected', 'sensor3'))

# Plot the time series comparison
ggplot(df_long_filtered, aes(x = timestamp, y = temperature, color = sensor, group = sensor)) +
  geom_line() + 
  scale_color_manual(values = c('sensor2' = 'green', 
                                'sensor2_corrected' = 'purple', 
                                'sensor3' = 'red')) + 
  labs(title = 'Time Series of Water Temperature from Sensors', 
       x = 'Timestamp', y = 'Temperature (°C)', color = 'Sensors') +
  theme_minimal() +
  theme(legend.position = 'top')
```

## Conclusion

The correction of **Sensor 2** to reflect **Sensor 3** was successful based on the regression model. The performance metrics indicate a good fit of the model, and the residual plot shows no major issues with the correction process. The corrected values of **Sensor 2** are now more consistent with **Sensor 3** and can be used for further analysis.

## Next Steps

- Further validation with additional data.
- Explore other correction models (e.g., polynomial regression) if needed.
