---
title: "Lull Creek QAQC"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE)
# Explanation of code
## Action required

#Install and/or load packages
#install.packages('ggplot2')
#install.packages('plotly')
#install.packages('tidyverse')

library(ggplot2)
library(plotly)
library(tidyverse)
library(knitr)
library(lubridate)

## Set working directory
opts_knit$set(root.dir = "~/git-repos/wx-tools/data_output/")
```


```{r load rain data, include=FALSE}

# Load data - read headers
fileheaders <- read.csv("2023-10-04.5minuteSamples_lullftqc.csv",
                        nrows = 1, as.is = TRUE,
                        header = FALSE)
# Read in data, drop redundant header rows
df <- read.csv("2023-10-04.5minuteSamples_lullftqc.csv",
                 header = FALSE,
                 skip = 4,
                 stringsAsFactors = FALSE)

# Add headers to dataframe
colnames(df) <- fileheaders
names(df)
glimpse(df)

colnames(df)[1] <- "Date"
df$Date<-as.POSIXct(df$Date,format="%Y-%m-%d %H:%M")

#check structure
str(df)
```


```{r qc_flagging, include = FALSE}

data_flagged<-df %>% 
    mutate(temp_diff = lead(TWtrLULL1PT_Avg)-lag(TWtrLULL1PT_Avg),
           depth_diff= lead(DepthLULL1PT_Avg)-lag(DepthLULL1PT_Avg),
           qc_flag = case_when(is.na(DepthLULL1PT_Avg) ~ "MV: QC'd by EH"
                               ,TWtrLULL1PT_Avg >= 25 ~ "SVC: Max temp: QC'd by EH"
                               ,TWtrLULL1PT_Avg < 0 ~ "SVC: Min temp: QC'd by EH"
                               ,temp_diff > 1 ~ "SVC: Rate of change exceedance Temperature: QC'd by EH"
                               ,depth_diff > 1 ~ "SVC: Rate of change exceedance: QC'd by EH"
                               ,DepthLULL1PT_Avg < 0.03 ~  "SVC: Dewatering potential: QC'd by EH"
                               ,TRUE ~ "AV: QC'd by EH"))
       


data_SVC <- data_flagged %>% 
  filter(qc_flag == 'SVC')
data_MV <- data_flagged %>% 
  filter(qc_flag == 'MV')
data_AV <- data_flagged %>% 
  filter(qc_flag == 'AV')
```

## Overview

Two Onset Hobo U20L-04 pressure transducers (one measuring water pressure and one measuring air pressure) were installed 2018-08-23 to support the collection of baseline data for stream conditions. The sensors log on 10 minute intervals and are downloaded approximately 1 to 2 times per year. This dataset reflects the current time series and contains  `r nrow(data)` measurements of which `r nrow(data_SVC)` are flagged as suspicious (SVC), while `r nrow(data_AV)` are flagged as accepted (AV). Data is also stored and available for viewing on the Hakai sensor network.

`r paste("First created on 2023-04-27. Updated on", Sys.Date())`

## Site Metadata 

* 2019-04 installation removed due to extensive sediment buildup 
* 2019-09-30 installation re-installed by Hakai
* 2020 landslide at some point, telsepar knocked upwards and boulder it was mounted to was dislodged 
* 2020-02-27 last record of data until re-installed by Mamalilikulla 2020-06-08 
* 2020-08-22 download, sensor elevation change 
* 2020-10-16 download, sensor elevation change 
* 2021-08-11 download, sensor elevation change 
* 2021-09-29 Lull PT adjustments
* 2022-04-20 download
* 2022-08-02 download, sensor elevation change
* 2023-01-01 sensor memory full
* 2023-03-07 download 


##### Water Level
```{r plot-watlev, include=TRUE}

plot_ly(data_flagged, x = ~Date, y = ~DepthLULL1PT_Avg, 
        type = 'scatter', 
        mode = 'lines',
        text = ~flag,
        hovertemplate = paste('%{x}',
                        '%{text}', 
                        '%{y}',
                        '<extra></extra>'))%>%
  layout(title = " ", #barmode = 'stack',
         xaxis = list(title = "Date"),
         yaxis = list(side="left", title = 'Water Level [m]'))

         

```

##### Water Temperature
```{r plot-temp, include=TRUE}

plot_ly(data_flagged, x = ~Date, y = ~TWtrLULL1PT_Avg, 
               type = 'scatter', mode = 'lines', name = '', text = ~flag,
        hovertemplate = paste('%{x}',
                        '%{text}', 
                        '%{y}',
                        '<extra></extra>')) %>%
  layout(title = " ", #barmode = 'stack',
         xaxis = list(title = "Date"),
         yaxis = list(side="left", title = 'Water Temperature [degC]'))

```




